---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# superfundr

<!-- badges: start -->
[![Travis build Status](https://travis-ci.org/hepplerj/superfunds.svg?branch=master)](https://travis-ci.org/hepplerj/superfunds)
<!-- badges: end -->

The `superfundr` package contains data on U.S. Superfund sites established by the Environmental Protection Agency. 

Data is processed with the `tabulizer` package using the [most recent available PDF](https://www.epa.gov/superfund/superfund-data-and-reports) from the EPA.

## Installation

`superfundr` is a data package containing a dataset of Superfund sites in the United States. The best way to install it is through `devtools`.

### Install direct from GitHub

You can install the beta version of superfundr from [GitHub](https://github.com/hepplerj/superfundr) with:

``` r
devtools::install_github("hepplerj/superfundr")
```

## Loading the data

The package works best with the [tidyverse](http://tidyverse.org/) libraries and the [simple features](https://r-spatial.github.io/sf/index.html) package for mapping.

```{r libs}
library(tidyverse)
```

Load the data:

```{r load}
library(superfundr)
```

Look at it:

```{r look}
superfunds
```

## Contributing

We are an open source project. Want to help contribute? Open up an [issue](https://github.com/superfundr/resources/issues). Or, contribute your ideas, resources, and teaching material! To get started, take a look at [CONTRIBUTING.md](CONTRIBUTING.md).

## Code of Conduct

`superfundr` is committed to creating and supporting an inclusive community of practice. Please see our [Code of Conduct](CODE_OF_CONDUCT.md).

# Project Lead

Jason Heppler, PhD / University of Nebraska / t: @jaheppler g: @hepplerj
